\subsection{Working}
These steps are being followed throughout the project : 
\begin{enumerate}
    \item Analyzing the data of the CSV's received.
    \item Manipulating and predicting the meta data of CSV received.
    \item Segregation of the data.
    \item Conversion of CSV into the Graph Data by importing into the Neo4J.
    \item Pattern Analysis of sub-graphs.
    \begin{itemize}
        \item Clustering and Classification of the sub-graphs
        \item Analyzing the Graph for 6 degree separation.
        \item Optimal information to reach from one node to another.
    \end{itemize}
    \item Presenting Result
    \item Stating Conclusion
    
\end{enumerate}

\subsection{Phase 1}
These all checkpoints would be followed before the mid-term.

\subsubsection{Analyzing the data of the CSV’s received}

In this step, the raw data which is received through the sources would be cleaned up and the important aspects of the data is being analyzed and would be reported and kept as the possible major relations.

\subsubsection{Manipulating and predicting the meta data of CSV received}

Now, as the major feature of the data is being known, further exploration of those fields are being carried out.And also, finding or manipulating the details of the feature is being carried out in this phase.

\subsubsection{Segregation of the data}

Now, the data is being separated based on the meta-data produced in the second step. Now the data is ready to be exported to the graph database for further/advance analysis of the data.

\subsubsection{Conversion of CSV into the Graph Data by importing into the Neo4J}

In this step the refined data is being converted into graph structures with the help of cypher, wiz. the graph query language for Neo4J.All the relations for the graph are already present in the CSV which contains the details of edges.

\subsection{Phase2}

\paragraph{These all checkpoints would be presented in the end-term.}

\subsubsection{Pattern Analysis of sub-graphs}

In this section different graph analysis techniques are being applied into the database to find out the pattern in it. And also, bringing in the new facts and figures from it.

\subsubsection{Presenting Result}

Based on the prediction of the analysis the results are being figured out in this section

\subsubsection{Stating Conclusion}

Finally a conclusion has been made out which would be briefing the aim of the analysis and how much of it has being attained